Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-04 tex/results.tex
Add labels explanation on Fig 1

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$, for two mesh sizes as shown in the legend.}
    \label{fig:cube535}
 \end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{cubeL535nm_15Kvs19K.pdf} 
    \caption{Grid-independence study for a SiC cube of side $L=535$ nm submerged in air under a constant 
    electric field in the $z$-direction. The curves represent the extinction cross-section divided by $L^2$ 
    as a function of wavelength divided by $L$, for mesh sizes 19K = 19,200 triangles and 15K = 15,552 triangles. 
    The label "diff" refers to the difference between the results of the two meshes.}
    \label{fig:cube535}
 \end{figure}
